Assessing glymphatic transport velocities by adjoint methods

### 2018-10-12 tex/paper.tex
reelle data

The diffusivity of the Gadovist (600 Da) is currently not known {\colro{red} Geir vet dere?}, thus the diffusion of (Navn Gd-DPTA (550 Da)  will be used as reference. The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ , and obtained from [cite]. {\color{red} discussion om hvorfor eller nevne Stoke Einstein her?}

@@

The mesh construction was patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter. Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral. (BrainMesh code accessibility {\color{red} not fully tested}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh. The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.  
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\label{figmesh} 
\caption{A) Shows the mesh created from the baseline MR image with 3 domains. B) Shows the mesh created from the baseline MR image with 2 domains.  }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices.

@@

\subsection*{DTI comparison}
The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$. This is an increase from the reported values in [insert citation] of XX and XX.

>>>>

The diffusivity of the Gadovist (600 Da cite?) was estimated to be similar to the diffusion coefficient of Gd-DPTA (550 Da cite ?). This due to the fact that both molecules have similar mass/size, and based Stoke-Einstein equation should have similar diffusion coefficients. The free diffusion coefficient for Gd-DPTA  3.8e-5$\mathrm{mm\sp{2}/s}$ was obtained from [cite].

@@

The mesh construction was patient-specific and was constructed by using the MRI of a patient diagnosed with idiopathic normal pressure hydrocephalus (iNPH). The software Freesurfer was used in segmentation and creating the polyhedral surfaces of the white and grey matter. Then the use of T2 weighted MRI was used to segment the csf compartment surrounding the cerebral. The module BrainMesh (currently in testing) (BrainMesh code accessibility {\color{red} kan ta med eller bare si CGAL}) CGAL \cite{cgal:rty-m3-18b} was used to combine the polyhedral surfaces and to construed the mesh. The computational requirement for the resulting mesh was significant, therefore two submesh was also constructed, see Fig.\ref{Fig::Mesh}.
\begin{figure}
\centering
\includegraphics[scale=0.2]{mesh.png} 
\label{figmesh} 
\caption{A) Shows the mesh created from the baseline MR image with 3 domains. B) Shows the mesh created from the baseline MR image with 2 domains.  }
\label{Fig::Mesh}
\end{figure}
The 3 domain mesh in Fig.\ref{Fig::Mesh} A, consists of 244318 tetrahedral cells and 22057 vertices, while the 2 domain mesh Fig.\ref{Fig::Mesh} B consists of 335589 tetrahedral cells and 73002 vertices. The dimension of the mesh coordiantes are $\mathrm{mm}$.

@@

\subsection*{DTI comparison}
The median diffusion coefficient in the DTI was estimated to be respectively in white and grey matter to be 8.7e-4 $\mathrm{mm\sp{2}/s}$ and  1.0e-3 $\mathrm{mm\sp{2}/s}$. %This corresponds to 3.1 $\mathrm{mm\sp{2}/h}$ and  3.6 $\mathrm{mm\sp{2}/h}$. 
The self-diffusivity of water have been estimated to be about  3.0e-3$\mathrm{mm\sp{2}/s}$ at 37\sp{o}C.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$.

This is an increase from the reported values in [insert citation] of XX and XX.
